Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
paper beautification

Previous studies~\cite{gangli1} show that the FWL affects the poles and 
zeros positions, degrading the closed-loop dynamics, causing steady-state 
errors (see the Appendix~\ref{sec:appendix:LTIbackground} for details) 
and eventually destabilizing  the system~\cite{Bessa16}. However, since 
in this paper we require stability only as a precursor to safety, it is 
sufficient to check the (perturbed, noisy) model converges to a point 
within the safe states.

@@

To argue for this sufficient check, 
consider the set of initial states, $X_0$, which we assume to be convex since it's a hypercube. 
Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
\begin{align*}
x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
 \end{align*}     
where $x_k^i$ denotes the trajectories obtained from the single vertexes $v_i$.

@@

\item The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'{>}k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$. This is done according to the following argument.

A stable control system is known to have converging dynamics. 
Assume the closed-loop matrix eigenvalues are not repeated (which is sensible to do, since we select them). 
The distance of trajectories from the reference point (in this case the origin) decreases over time within subspaces related to real-valued eigenvalues. 
However, this in general not the case when dealing with complex eigenvalues.  
Consider the matrix $(A_d - B_d K)$, which updates the states every time step, and select eigenvalue with smallest (non trivial) imaginary value.  
call such value $\vartheta$. 
At every time interval $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
So surely taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
after $k$ steps we have completed a rotation. 
This is the completeness threshold.

\begin{figure*}[t]
\centering
\includegraphics[width=0.7\textwidth]{ct.eps}
\vspace{0.1cm}
\caption{Completeness threshold for multi-staged verification.}
\end{figure*}

@@

We have presented two approaches to synthesize state feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the system's dynamics 
up to the completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
Both approaches are novel in the control system literature in that it puts
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering the various error sources in the implementation 
of the control algorithm and in the computational modeling of plant dynamics.
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a reasonable
amount of time fully automatically.  In particular, both approaches
complement each other in the benchmark coverage and together 
solve all benchmarks provided in the set.
Future work will be the extension of these approaches to consider performance 
requirements while synthesizing digital controllers.

>>>>

Previous studies~\cite{gangli1} show that the FWL affects the poles and 
zeros positions, degrading the closed-loop dynamics, causing steady-state 
errors (see the Appendix~\ref{sec:appendix:LTIbackground} for details) 
and eventually destabilizing  the system~\cite{Bessa16}. However, since 
in this paper we require stability only as a precursor to safety, it is 
sufficient to check that the (perturbed, noisy) model converges to a neighbourhood of the equilibrium within the safe set.

@@

To argue for this sufficient check, 
consider the set of initial states, $X_0$, which we assume to be convex since it's a hypercube. 
Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
\begin{align*}
x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i 
      = \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
 \end{align*}     
where $x_k^i$ denotes the trajectories obtained from the single vertex $v_i$. 
We conclude that any $k$-step trajectory is encompassed, within a convex set, by those generated from the vertices.

@@

\item The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'{>}k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$. This is done according to the following argument, depicted in Fig \ref{fig:ct}.

A stable control system is known to have converging dynamics. 
Assume the closed-loop matrix eigenvalues are not repeated (which is sensible to do, since we select them). 
The distance of trajectories from the reference point (in this case the origin) decreases over time within subspaces related to real-valued eigenvalues;  
however, this in general not the case when dealing with complex eigenvalues.  
Consider the closed-loop matrix, which updates the states every discrete time step, 
and select the eigenvalue with smallest (non trivial) imaginary value -- call such value $\vartheta$. 
At every consecutive time steps $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
So taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
surely after $k$ steps we have completed a full rotation, which results in a point that is closer to the origin. 
This $k$ is then taken to be the completeness threshold.

\begin{figure*}[t]
\centering
\includegraphics[width=0.7\textwidth]{ct.eps}
\vspace{0.1cm}
\caption{Completeness threshold for multi-staged verification.}
\label{fig:ct}
\end{figure*}

@@
